\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.35in}
\addtolength{\evensidemargin}{-0.35in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Chenghao Li} \\ \vspace{6pt}
    \small (408)256-3278 $||$ \href{mailto:chenghaoli36@berkeley.edu}{{chenghaoli36@berkeley.edu}} $||$ 
    \href{https://linkedin.com/in/li-chenghao/}{{linkedin.com/in/li-chenghao}} $||$
    \href{https://github.com/xa1on}{{github.com/xa1on}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley (Data Science)}{Berkeley, CA}
      {Advanced CS Structures/Data Structures \& Algorithms - Foundations, Probability, Principles of DS.}{Present -- 2026}
    \resumeSubheading
      {Foothill College / San Jose City College (Computer Science, Physics, Math)}{Los Altos, CA}
      {Data Structures \& Algorithms (C++, Python, Java) - Comp Architecture - Discrete Math.}{Dual Enrolled}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {OCF Board of Directors (Open Computing Facility)}{2024 -- Present}
      {UC Berkeley}{Berkeley, CA}
      \resumeItemListStart
        \resumeItem{Assisted the administration of Linux infrastructure serving petabytes of data annually for 80K+ students and faculty.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Lead Developer}{2022 -- Present}
      {Archaic}{}
      \resumeItemListStart
        \resumeItem{Developed open-source OpenCV/FFmpeg based tools and GUI libraries while providing support for and maintaining projects/tools utilized by 1000+ users.}
        \resumeItem{Contributed 37K+ lines of code as the sole developer of all projects in the organization GitHub.}
    \resumeItemListEnd

    \resumeSubheading
      {Hacakathon Logistics}{2021 -- 2022}
      {ThetaHacks}{}
      \resumeItemListStart
        \resumeItem{Organized the hackathon as part of the logistics team serving 500+ attendees.}
      \resumeItemListEnd

    \resumeSubheading
      {Robotics Programming Lead \& Team Lead}{2018 -- 2023}
      {Milpitas Xtreme Robotics (MXR)}{Milpitas, CA}
      \resumeItemListStart
        \resumeItem{Co-founder of the MXR VEX Robotics Competition team(1669X), now one of the most competitive high school robotics organizations in the state with worlds qualifications 4 years in a row.}
        \resumeItem{Earned the team their first award and worlds qualification in over a decade within a year of joining the team.}
        \resumeItem{Mentored 100+ students to help further their interest in STEM-related subjects.}
        \resumeItem{Represented and developed for the team while attending multiple hackathons, including ProHacks, BridgeHacks, DubHacks, SigmaHacks, DVHacks, and more, winning additional awards for the organization.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Depth-Anything-TensorRT Contributions} $|$ \emph{C++, Python, ONNX, TensorRT, OpenCV.}}{2024 -- 2025}
        \resumeItemListStart
          \resumeItem{Developed a command line interface to improve functionality and ease of use for a TensorRT port of a monocular depth estimation model (DepthAnythingV2/V1).}
        \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Prorecs} $|$ \emph{Batch, FFmpeg.}}{2021 -- 2022}
          \resumeItemListStart
            \resumeItem{Engineered a FFmpeg based video processing tool capable of batch encoding videos and image sequences with batch frontend and backend.}
            \resumeItem{Implemented custom config system with support for all FFmpeg compatible codecs.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{RBLXMVM} $|$ \emph{C++, Lua.}}{2019 -- 2023}
          \resumeItemListStart
            \resumeItem{Designed, invented and supported an entire suite of game engine tools from scratch.}
            \resumeItem{Published plugins which generated 1000+ sales.}
            \resumeItem{Utilized cubic/bezier interpolation methods to generate seemless camera paths.}
            \resumeItem{Integrated plugins into other codebases with reverse engineering strategies when no documentation was available.}
            \resumeItem{Created an open-source GUI library from scratch.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
     \small{\item{
     \textbf{Robotics}{: \href{https://www.musd.org/district-news/milpitas-xtreme-robotics-team-wins-state-championship-advances-to-world-competition}{\underline{VRC State Tournament Champion, Skills Champion, Excellence Award, Design Award.}}} \\
     \textbf{Hacakthons}{: ProHacks 1st place, Best Use of Google API(DialogFlow) DubHacks.} \\
    }}
 \end{itemize}



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript (NodeJS), C\#, HTML/CSS.} \\
     \textbf{Frameworks}{: OpenCV, React, Express, FFmpeg, Flutter, BLAS, Pandas, Numpy, MongoDB.} \\
     \textbf{Developer Tools}{: Git, VS Code, PyCharm, IntelliJ, Eclipse, AutoCAD.} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}